EagerNet: Early Predictions of Neural Networks for Computationally Efficient Intrusion Detection

### 2020-07-23 paper/paper.tex
Small changes

Training the weights connecting a layer to the next output neuron can also be achieved by considering only the loss of that particular layer/output which turns out to be a pure logistic regression between the $p^{th}$ layer and the $(p+1)^{th}$ layer's output neuron. Nevertheless, due to the difficulty of the problem, constructing a linear combination of intermediate logits with adjustable weights provides limited mappings, and therefore inaccurate predictions, because the loss never completely converges. Back-propagating all losses at once is thus important and helps to update the weights of the network at the same time as adjusting the weights of the output neurons, thereby allowing the neural network to distribute the knowledge across all weights and, make accurate predictions at each layer.

@@

This paper explores the early termination of the viability of the \glspl{fcnn} test. We propose EagerNet, an architecture that allows predictions to be made as soon as the neural network is sufficiently confident, saving energy and resources and making it possible to implement similar architectures in real-time applications where prediction speed is relevant. We evaluate our approach using two intrusion detection datasets and obtain satisfactory results indicating the possibility of achieving comparable evaluation scores to traditional \glspl{fcnn} yet using only a segment of the neural network, as most network traffic flows are simpler to classify and only a minority need deeper propagation.
Furthermore, we show that by setting a confidence threshold during deployment, it becomes possible to trade accuracy for resources usage and energy consumption. The EagerNet architecture is thus characterized by its simplicity and effectiveness, making it an ideal solution for potential \gls{fcnn}-based \glspl{ids} whenever resources are of primary concern.

>>>>

Instead of backpropagating each loss through all layers, it is also possible to only backpropagate each loss of the intermediate layers only to the previous layer but not until the beginning. Only the last layer's output's loss would then be backpropagated until the beginning but the other intermediate output's losses only one step. One benefit of this would be to save computational resources during training. Our results showed that this method results in worse accuracy for the intermediate layers' outputs. Backpropagating all losses at once is thus important and helps to update the weights of the network at the same time as adjusting the weights of the output neurons, thereby allowing the neural network to distribute the knowledge across all weights and make accurate predictions at each layer.

@@

This paper explores if it is viable to terminate the evaluation of \glspl{fcnn} before the final layer to save computational resources. We propose EagerNet, an architecture that allows predictions to be made as soon as the neural network is sufficiently confident, saving energy and resources and making it possible to implement similar architectures in real-time applications where prediction speed is relevant. We evaluate our approach using two intrusion detection datasets and obtain satisfactory results indicating the possibility of achieving comparable evaluation scores to traditional \glspl{fcnn} yet using only a segment of the neural network, as most network traffic flows are simpler to classify and only a minority need deeper propagation through the neural network.
Furthermore, we show that by setting a confidence threshold during deployment, it becomes possible to trade accuracy for resources usage and energy consumption. The EagerNet architecture is thus characterized by its simplicity and effectiveness, making it an ideal solution for potential \gls{fcnn}-based \glspl{ids} whenever resources are of primary concern.
